### 2011-05-12 paper.tex
Added notes about basic operator properties

@@

\begin{theorem}\label{amplify}
Let $C$ be a well-structured complexity class. Then \emph{$\bp \cdot C = \bp \parity C$}.
\end{theorem}

>>>>

\section{Basic Operator Results}

Because we will be working with complexity classes defined by sequences of operators applied to $\p$, it will be useful to have several basic results about manipulations that can be performed with operators. We will start with the ability to collapse two identical operators into one.

\begin{prop}\label{collapse}
Let $C$ be a complexity class. Then $\Sigma\cdot\Sigma\cdot C = \Sigma\cdot C$, $\Pi\cdot\Pi\cdot C = \Pi\cdot C$, and $\strongbp\cdot\strongbp\cdot C = \strongbp \cdot C$.
\end{prop}

We will also use the following results that allow in one direction the interchanging of $\strongbp$ with the other operators.

\begin{prop}\label{interchange}
Let $C$ be a complexity class. Then $\Sigma\cdot\strongbp\cdot C \subseteq \strongbp\cdot\Sigma\cdot C$, $\Pi\cdot\strongbp\cdot C \subseteq \strongbp\cdot\Pi\cdot C$, and $\parity\cdot\strongbp\cdot C \subseteq \strongbp\cdot\parity\cdot C$.
\end{prop}

All of these results are not difficult to verify.

@@

\begin{theorem}\label{amplify}
Let $C$ be a well-structured complexity class. Then \emph{$\bp \cdot C = \strongbp \cdot C$}.
\end{theorem}
